%        File: 22NovMeeting.tex
%     Created: Mon Nov 21 04:00 PM 2016 E
% Last Change: Mon Nov 21 04:00 PM 2016 E
%
% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}

\usepackage[margin=1in]{geometry}
\usepackage[backend=biber,style=authoryear-comp,useprefix=false]{biblatex}

\usepackage{stmaryrd}
\usepackage[]{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{forest}
\usepackage{tabularx}
\usepackage{linguex}
\usepackage{centernot}

\useforestlibrary{linguistics}
\forestset{tree defaults/.style={for tree={parent anchor=south, child anchor=north},every tree node/.style={align=center,anchor=north},level/.style={sibling distance=50mm/#1},baseline}}

\forestset{en/.style={parent anchor=center, child anchor=center}}
\forestset{em/.style={parent anchor=north west, child anchor=north west}}
\forestset{el/.style={parent anchor=north, child anchor=north}}

\usetikzlibrary{positioning}
\DeclareNameFormat{labelname:poss}{% Based on labelname from biblatex.def
  \ifcase\value{uniquename}%
  \usebibmacro{name:last}{#1}{#3}{#5}{#7}%
  \or
  \ifuseprefix
  {\usebibmacro{name:first-last}{#1}{#4}{#5}{#8}}
  {\usebibmacro{name:first-last}{#1}{#4}{#6}{#8}}%
  \or
  \usebibmacro{name:first-last}{#1}{#3}{#5}{#7}%
  \fi
  \usebibmacro{name:andothers}%
  \ifnumequal{\value{listcount}}{\value{liststop}}{'s}{}
}

\DeclareFieldFormat{shorthand:poss}{%
  \ifnameundef{labelname}{#1's}{#1}
}

\DeclareFieldFormat{citetitle:poss}{\mkbibemph{#1}'s}

\DeclareFieldFormat{label:poss}{#1's}

\newrobustcmd*{\posscitealias}{%
  \AtNextCite{%
    \DeclareNameAlias{labelname}{labelname:poss}%
    \DeclareFieldAlias{shorthand}{shorthand:poss}%
    \DeclareFieldAlias{citetitle}{citetitle:poss}%
    \DeclareFieldAlias{label}{label:poss}
  }
}

\newrobustcmd*{\posscite}{%
  \posscitealias%
  \textcite
}

\newrobustcmd*{\Posscite}{\bibsentence\posscite}

\newrobustcmd*{\posscites}{%
  \posscitealias%
  \textcites
}

\newcommand\quelle[1]{{%
  \unskip\nobreak\hfil\penalty50
  \hskip2em\hbox{}\nobreak\hfil#1%
  \parfillskip=0pt \finalhyphendemerits=0 \par
}
}

\bibliography{Thesis}
\title{Meeting Notes}
\author{Dan Milway}
\begin{document}
\maketitle

\section{The Problem}
\ex. \textbf{Adjunct Control}
\a. John$_i$ heard Mary without PRO$_j$ seeing her.
\b.{\small
\begin{forest}
  baseline,nice empty nodes,sn edges
  [TP
    [John,name=Spec TP]
    [
      [T]
      [
	[vP
	  [$\langle$John$\rangle$,name=Spec vP]
	  [
	    [v]
	    [VP]
	  ]
	]
	[PP
	  [without]
	  [ProgP
	    [$\langle$John$\rangle$,name=Spec ProgP] 
	      [Prog$^\prime$[seeing her,roof]]
	  ]
	]
      ]
    ]
  ]
  %\draw[->] (Spec ProgP) to[out=south west, in=south] (Spec vP);
  %\draw[->] (Spec vP) to[out=south west, in=south west] (Spec TP);
\end{forest}}

\ex. \textbf{*French Resultatives}
\a.* John hammered the metal$_i$ \textit{res}$^\circ$ PRO$_i$ flat.
\b.{\small
\begin{forest}
  baseline,nice empty nodes,sn edges
  [AgrOP
    [metal,name=Obj]
    [
      [AgrO]
      [
	[VP
	  [hammered]
	  [$\langle$metal$\rangle$,name=V Theme]
	]
	[resP
	  [res$^\circ$]
	  [SC
	    [$\langle$metal$\rangle$,name=A Theme]
	    [flat]
	  ]
	]
      ]
    ]
  ]
  %\draw[->] (A Theme) to[out=south west, in=south] (V Theme);
  %\draw[->] (V Theme) to[out=south west, in=south] (Obj);
\end{forest}}

\begin{itemize}
  \item \LLast[b] and \Last[b] are isomorphic.
  \item SWM from [Spec Prog] to [Spec vP] in \LLast[b] is allowed.
  \item SWM from the SC to [Comp V] in \Last[b] is disallowed.
  \item \textcite{hornstein2001move} argues that SWM in \LLast is okay since PP is not a ``bounding node'' (\textit{i.e.}, not a phase).
  \item The DP only crosses one \textit{barrier} (the adjunction site).
  \item Assuming resP is a phase, SWM in \Last crosses two \textit{barriers} (the resP phase and the adjunction site), making it an illicit move.
\end{itemize}
\section{P is not a phase head}
\begin{itemize}
  \item Abels' (\citeyear{abels2003successive}) account of adposition stranding relies heavily on the possibility of P$^\circ$ being a phase head.
    \begin{itemize}
      \item For Abels there is a parameter: ``P$^\circ$ is \{not\} a phase head.''
    \end{itemize}
  \item \textcite{chomsky2008on} argues that the choice of CP and v*P as phases due to interface requirements.
  \item Since interfaces are fixed (\textit{i.e.}, not parameterized), the choice of phase heads must be fixed.
  \item Phases are semantically complete (v*P is $\Theta$-complete, CP is propositionally complete)
  \item PPs are usually predicative, and therefore not complete.
\end{itemize}
\subsection{Questions}
\begin{itemize}
  \item How do we account for the facts of P-stranding?
  \item P-stranding $\rightarrow$ Directionalized locatives (\textit{e.g.}, English, PEI French)
  \item Directionalized Locatives $\centernot\rightarrow$ P-stranding (\textit{e.g.}, German)
\end{itemize}
\section{resP is a phase}
\begin{itemize}
  \item resP is $\Theta$-complete
  \item How is the resP in \Last related to \textit{flatten the metal}?
\end{itemize}
\end{document}


