%        File: 28AprilMeeting.tex
%     Created: Fri Apr 28 10:00 AM 2017 E
% Last Change: Fri Apr 28 10:00 AM 2017 E
%
% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}

\usepackage[margin=1in]{geometry}
\usepackage[backend=biber,style=authoryear-comp,useprefix=false]{biblatex}

\usepackage{stmaryrd}
\usepackage[]{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{forest}
\usepackage{tabularx}
\usepackage{linguex}
\usepackage{centernot}
\usepackage[normalem]{ulem}

\addbibresource{Thesis.bib}
\begin{document}
\begin{itemize}
  \item Snyder: Languages that allow Bare Stem Compounding also allow Resultatives.
  \item In his thesis he argues for a macroparameter over a lexical parameter.
  \item The latest iteration of his parameter is a rule of semantic composition whose availability in a given languages is parameterized.
\end{itemize}
\ex. Generalized Modification (GM)\\
If $\alpha$ and $\beta$ are syntactic sisters under the node $\gamma$, where $\alpha$ is the \uline{head} of $\gamma$, and if $\alpha$ denotes a \uline{kind}, then interpret $\gamma$ semantically as a \uline{subtype} of $\alpha$'s kind that stands in a pragmatically suitable \uline{relation} to the denotation of $\beta$
\parencite[][underlining Snyder's]{snyder2012parameter}

\begin{itemize}
  \item \textit{e.g.}, a \textit{banana box} is a subtype of the \textsc{box} kind which stands in a pragmatically suitable relation to bananas.
  \item This is problematic:
    \begin{enumerate}
      \item It doesn't fully capture compounds
      \item Parameterizing composition makes the acquisition task harder
      \item GM is not a well-formed rule of composition
      \item Something like GM is part of PM and FA
    \end{enumerate}
\end{itemize}
\ex. \textbf{Non-kind-denoting compounds}
\a. relationship George
\b. weekend Michela
\b. semantics Heather

\ex. \textbf{Are Bare Stems kind-denoting?}
\a. Dog*(-s) are fun.
\b. *(The) dodo is extinct.
\c. Water(*-s) is/*are essential.

\ex. \textbf{PM involves something like GM}
\a. a red dress
\b. red hair
\c. red clay
\d. a red cent
\e. a red Liberal

\ex. \textbf{FA involves something like GM}
\a. boil the water
\b. boil a potato

\end{document}


