%        File: ArgSharingIsntECM.tex
%     Created: Thu Jun 09 03:00 PM 2016 E
% Last Change: Thu Jun 09 03:00 PM 2016 E
%
% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}

\usepackage[margin=1in]{geometry}
\usepackage[backend=biber,style=authoryear-comp,useprefix=false]{biblatex}

\usepackage{stmaryrd}
\usepackage[]{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{forest}
\usepackage{tabularx}
\usepackage{linguex}
\usepackage{centernot}

\begin{document}
Argument sharing constructions, such as adjectival resultatives (ARs), directionalized Locatives (DLs), and direct perception reports (DPRs), bear a striking similarity to ECM constructions.

\ex.
\a. James punched the boxer unconscious. (AR)
\b. Alice kicked the ball between the pylons (DLs)
\c. Gerard saw the goose fighting the eagle. (DPRs)

\ex. I consider Marc (to be) intelligent. (ECM)

In both types of constructions, the subjects of lower clauses or clause-like constituents have accusative case licensed by the verb of the higher clause.

\section{Object position}
The two construction types are similar in that subject of the lower clause raises to object position in the higher clause.
In this section I will show that transitive objects, ECM subjects, and shared arguments are all in the same structural position.

\subsection{Shared Arguments C-Command VP adjuncts}
Evidence for shared arguments being direct objects of the higher clause come from the fact that they appear to c-command VP adjucts, just as transitive objects and ECM subjects do.
C-command can be demonstrated by the fact that shared arguments license NPI's in VP adjuncts and bind into VP adjuncts.
Furthermore, quantifier scope facts are consistent with this claim.

Note that shared argument pronouns and R-expressions in VP adjuncts cannot co-refer, as demonstrated in \Next, due to a condition C violation.

\ex.
\a.* Sonya painted his$_i$ wall red without Bill's$_i$ permission.
\b.* Robert threw her$_i$ ball behind the house without Sonya's$_i$ premission.
\c.* I [saw her$_i$ [planting flowers] [through Mary's$_i$ telescope]] 

Shared arguments can also bind anaphors in VP adjuncts as in \Next.
\ex.
\a. Fred knocked the two men unconscious with each other's bats.
\b. Jill hit the two girls' balls over the fence with each other's bats.
\c. I saw the two boys planting flowers through each other's telescopes.

These binding patterns parallel those in ECM constructions, and those of transitive objects, which suggests that shared arguments are in direct object position.

\end{document}


