%        File: CCommand.tex
%     Created: Thu Jun 02 11:00 AM 2016 E
% Last Change: Thu Jun 02 11:00 AM 2016 E
%
% arara: pdflatex
% arara: biber
% arara: pdflatex
% arara: pdflatex
\documentclass[letterpaper]{article}

\usepackage[margin=1in]{geometry}
\usepackage[backend=biber,style=authoryear-comp,useprefix=false]{biblatex}

\usepackage{stmaryrd}
\usepackage[]{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{forest}
\usepackage{tabularx}
\usepackage{linguex}
\usepackage{centernot}
\title{Meeting Notes}
\author{Dan Milway}
\bibliography{Thesis}
\begin{document}
\maketitle

\ex. I painted $[$the wall$]_i [ t_i$ red$]]$.

\ex. I kicked $[$the ball$]_i [ t_i$ into the net$]$.

\ex. I saw $[$a comet$]_i [ t_i$ passing Saturn$]$.

\section{Where is the ``Object''}
\begin{itemize}
  \item Theta considerations suggest that it is in ``Spec Pred'' and ``Comp V''
  \item Does it raise to Object position? (Spec Agr$_o$ in \textcite{lasnik1999minimalist})
    \begin{itemize}
      \item does it c-command VP adjuncts?
    \end{itemize}
\end{itemize}
\subsection{Condition C}
\ex.
\a.* I painted his$_i$ wall red without John$_i$'s permission.
\b.* I painted his$_i$ wall without John$_i$'s permission.

\subsection{Condition A}
\ex.
\a.? I painted the two men red with each other's paintbrushes
\b. I painted the two men with each other's paintbrushes

\subsection{NPI licensing}
\ex.
\a.?* I painted no wall red with any brush.
\b.? I painted no wall with any brush.

(Scope???)

\section{Stray thoughts}
\begin{itemize}
  \item Given a sideward movement story, It's not clear where the Object is base generated
    \begin{itemize}
      \item (1) Build PredP, (2) Move Object to Comp V
      \item (2) Merge(V, Object), (2) build PredP, (3) Move object to Spec Pred
    \end{itemize}
  \item Romance has [\textit{consider} SC] constructions, What is the position of the Accusative DP there?
  \item Those constructions in Romance that allow argument sharing involve non-agreeing/``light''/particle-y items intervening between the shared argument and the lower predicate.
    \begin{itemize}
      \item Resultatives: \textit{peint les murs \textbf{en} blanc}
      \item Pseudorelatives: \textsc{arg} C$^0$ \textsc{pred}
    \end{itemize}
\end{itemize}

\end{document}


