% arara: pdflatex: {options: "-draftmode"}
% arara: biber
% arara: pdflatex: {options: "-draftmode"}
% arara: pdflatex: {options: "-file-line-error-style"}
\documentclass[MilwayThesis]{subfiles}
\setcounter{chapter}{5}

\begin{document}
\epigraph{All happy families are alike; every unhappy family is unhappy in its own way.}{\textit{Anna Karenina}\\\textsc{Leo Tolstoy}}
So far, I have proposed a theory of syntax, a structural analysis of resultatives, and an analysis of the resultative parameter.
Although they share a justification in minimalism, each of these is an independant proposal, and as such their combination must be justified.
In this chapter I show that the combination of my proposals work together.
I do so by first showing that the structure in \Next can be derived in a language with uninflected adjectives ($adj_\emptyset \in \textsc{lex}$), and then by showing how such a derivation fails in a language without uninflected adjectives ($adj_\emptyset \centernot\in \textsc{lex}$).
\ex.
{\small
\begin{forest}
    nice empty nodes,sn edges,baseline,
%    for tree={
%    calign=fixed edge angles,
%    calign primary angle=-30,calign secondary angle=60}
    [VP
	    [VP
		    [hammer]
		    [DP[the metal,roof,name=compV]]
	    ]
	    [resP
		    [$\langle$DP$\rangle$,name=specRes]
		    [
			    [res]
			    [SC
				    [$\langle$DP$\rangle$,name=SCDP]
				    [
					    [adj]
					    [\textsc{flat}]
				    ]
			    ]
		    ]
	    ]
    ]
    \draw[->] (SCDP) to[out=south west, in=south] (specRes);
    \draw[->] (specRes) to[out=south, in=south east] (compV);
\end{forest}
}

In the first section, I will describe a derivation of the English resultative VP \textit{hammer the metal flat} and show that it converges at the CI interface (taking SM convergence for granted).
In the second section, I will describe two derivations of the ungrammatical French resultative VP \textit{marteller le m\'etal plat}, and show that deriving that VP leads to a CI crash, while avoiding that crash blocks the derivation.

Before describing the derivations, I will reiterate and clarify my assumptions regarding the nature of the syntactic derivation.
I will adopt a slightly simplified version of the formal grammar developed by \textcite{collins2016formalization} which I will augment slightly based on new assumptions.
A \textit{derivation} is defined as a finite sequence of \textit{stages}, $\langle S_1, S_2 \ldots S_n\rangle$.
Each stage $S_i$ in a derivation is a pair $\langle LA_i, W_i\rangle$, where $LA_i$ is a set of lexical items called the \textit{lexical array} and $W_i$ is a set of syntactic objects called the \textit{workspace}.
The computational operations (Merge, Select, Copy, Transfer) play the role that rules on inference play in deductive systems, that is, they map derivational stages onto subsequent stages.
A given stage $S_i$ \textit{derives} a subsequent stage $S_{i+1}$ if and only if some operation, applied to $S_i$, yields $S_{i+1}$.


\section{A successful derivation in English}
In many ways, successful derivations, like happy families, are uninteresting, but they still must be demonstrated in order to show where the crashing derivations go wrong.

To begin with, we derive the result phrase.
The formal derivation and resulting unlabelled structure is given in \Next.
\ex.
\a.
\begin{tabular}[t]{llll}
	\textbf{Stage} & \textbf{LA} & \textbf{Workspace} & \\
	\cline{1-3}
	1 & $
	\begin{Bmatrix*}[l]
		\sqrt{\textsc{flat}},\\
		adj_\emptyset,\\
		res,\\
		\text{DP}
	\end{Bmatrix*}
	$ & $\emptyset$ & Select($\sqrt{\textsc{flat}}$)\\
	2 & $
	\begin{Bmatrix*}[l]
		adj_\emptyset,\\
		res,\\
		\text{DP}
	\end{Bmatrix*}
	$ & $\left\{\sqrt{\textsc{flat}}\right\}$ & Select($adj_\emptyset$)\\
	3 & $
	\begin{Bmatrix*}[l]
		res,\\
		\text{DP}
	\end{Bmatrix*}
	$ & $
	\begin{Bmatrix*}[l]
		adj_\emptyset,\\
		\sqrt{\textsc{flat}}
	\end{Bmatrix*}$
	& Merge($adj_\emptyset, \sqrt{\textsc{flat}}$)\\
	4 & $
	\begin{Bmatrix*}[l]
		res,\\
		\text{DP}
	\end{Bmatrix*}
	$ & $\left\{ \left\{_\alpha adj_\emptyset, \sqrt{\textsc{flat}} \right\} \right\}$ & Select(DP)\\
	5 & $\left\{ res \right\}$ & $
	\begin{Bmatrix*}[l]
		\text{DP},\\
		\left\{_\alpha adj_\emptyset, \sqrt{\textsc{flat}} \right\}
	\end{Bmatrix*}
	$ & Merge(DP, $\alpha$)\\
	6 & $\left\{ res \right\}$ & $ \left\{ \left\{_\beta \text{DP}, \left\{_\alpha adj_\emptyset, \sqrt{\textsc{flat}} \right\} \right\} \right\}$ &
	Select(\textit{res})\\
	7 & $\emptyset$ & $
	\begin{Bmatrix*}[l]
		res,\\
		\left\{_\beta \text{DP}, \left\{_\alpha adj_\emptyset, \sqrt{\textsc{flat}} \right\} \right\}
	\end{Bmatrix*}
	$ & Merge(\textit{res}, $\beta$)\\
	8 & $\emptyset$ & $\left\{ \left\{_\gamma res, \left\{_\beta \text{DP}, \left\{_\alpha adj_\emptyset, \sqrt{\textsc{flat}} \right\} \right\}\right\} \right\}$
	& Copy(DP)\\
	9 & $\emptyset$ & $
	\begin{Bmatrix*}[l]
		\text{DP},\\
		\left\{_\gamma res, \left\{_\beta \text{DP}, \left\{_\alpha adj_\emptyset, \sqrt{\textsc{flat}} \right\} \right\}\right\}
	\end{Bmatrix*}
	$
	& Merge(DP, $\gamma$)\\
	10 & $\emptyset$ & $
	\left\{\left\{_\delta \text{DP},\left\{_\gamma res, \left\{_\beta \text{DP}, \left\{_\alpha adj_\emptyset, \sqrt{\textsc{flat}} \right\} \right\}\right\}\right\}\right\}
	$
	& Transfer($\beta$)\\
\end{tabular}
\b.
{\small
  \begin{forest}
      nice empty nodes,sn edges,baseline,for tree={
    calign=fixed edge angles,
  calign primary angle=-30,calign secondary angle=70}
      [$\delta$
        [DP$_\varphi$[{\rm the metal},roof]]
        [$\gamma$
          [res]
          [$\beta$
        [DP$_\varphi$[{\rm the metal},name=SC DP,roof]]
        [$\alpha$
          [adj$_\emptyset$]
          [{\rm flat}]
        ]
          ]
        ]
      ]
      \draw[thick] ([xshift=-36pt, yshift=-24pt]SC DP) arc[start angle=170,end angle=130,radius=7.5cm];
  \end{forest}
}

Assuming res is a phase head, its complement $\beta$ is trasferred and must be labelled along with the SOs contained in $\beta$.
The small clause $\beta$ ($\left\{_\beta \langle \text{DP}\rangle, \left\{_\alpha adj_\emptyset, \sqrt{\textsc{flat}} \right\} \right\}$) is a Phrase-Phrase structure, but since one of its constituent parts, the DP, is a lower copy, that part is invisible to the labelling algorithm.
Therefore, only the adjective ($\left\{_\alpha adj_\emptyset, \sqrt{\textsc{flat}} \right\}$) is available to provide a label.
Assuming roots are inert for labelling, and uninflected categorizing heads are able to label, the label of $\alpha$, and therefore the label of $\beta$, is $adj_\emptyset$.
So, $\beta$ is succesfully labelled and therefore convergent at the CI interface.
\ex. LA($\left\{_\beta \langle\text{DP}\rangle, \left\{_\alpha adj_\emptyset, \sqrt{\textsc{flat}} \right\} \right\} = \left[_{adj} \langle\text{DP}\rangle, \left[_{adj} adj_\emptyset, \sqrt{\textsc{flat}} \right]  \right]$


\section{Two crashing derivations in French}

\subsection{Crashing Derivation \#1}

\subsection{Crashing Derivation \#2}

\end{document}
