%        File: AC.tex
%     Created: Thu Jan 26 04:00 PM 2017 E
% Last Change: Thu Jan 26 04:00 PM 2017 E
%
% arara: pdflatex: {options: "-draftmode"}
% arara: biber
% arara: pdflatex: {options: "-draftmode"}
% arara: pdflatex: {options: "-file-line-error-style"}
\documentclass[proposal]{subfiles}

\begin{document}
\begin{frame}
  {What can this version of Label Theory get us?}
  \begin{block}
    {Subjects of ACC-ing clauses and pseudo-relatives}
    \begin{itemize}
      \item<2-> \textcite{cinque1996pseudo} shows that the position of an ACC-ing/pseudo-relative clause affects the behaviour of its subject.
    \end{itemize}
    \only<2->{
    \ex. \textbf{Italian pseudo-relative (PR)}\\
    {\rm Mario che correva a tutti velocit\`a}

    \ex. \textbf{English ACC-ing clause (AC)}\\
    {\rm Mario running at full speed}

  }
    \begin{itemize}
      \item<3-> If the AC/PR is a complement of V, the subject cannot move.
      \item<3-> If the AC/PR is a VP adjunct, the subject must move.
    \end{itemize}
  \end{block}
\end{frame}
\begin{frame}
  {What can this version of Label Theory get us?}

    \begin{columns}
    \begin{column}[T]{0.6\textwidth}
      {\rm *Mario$_i$ was [$_{VP}$ [heard [$t_i$ being slandered]]]}
      \begin{block}
	{Complement ACs}
	\begin{itemize}
	  \item Subject is frozen in the AC
	  \item Prog$^\circ$ is too weak to label $\zeta$
	    \begin{itemize}
	      \item Compare Chomsky's (2015) discussion of EPP
	    \end{itemize}
	  \item If {\rm Mario} were \textit{in situ}, Label($\zeta$) = $\langle\text{F,F}\rangle$
	  \item Lower copies are invisible, so $\zeta$ is unabelable.
	  \item The derivation crashes at CI
	\end{itemize}
      \end{block}
    \end{column}
    \begin{column}[T]{0.4\textwidth}
	{\small
	  \begin{forest}
	    nice empty nodes,sn edges,baseline
	    [$\alpha$
	      [{\rm Mario}]
	      [$\beta$
		[T]
		[$\gamma$
		  [Voice$_{pass}$]
		  [$\delta$
		    [{\rm hear}]
		    [$\zeta$
		      [$\langle${\rm Mario}$\rangle$]
		      [Prog]
		    ]
		  ]
		]
	      ]
	    ]
	  \end{forest}
	}
    \end{column}
  \end{columns}
\end{frame}
\begin{frame}
  {What can this version of Label Theory get us?}
  \begin{columns}
    \begin{column}[T]{0.55\textwidth}
      {\rm *I [ [$_{VP}$ saw Bill] [Mario running]]}
      \begin{block}
	{Adjunct ACs}
	\begin{itemize}
	  \item Subjects must move to theme position
	  \item $\eta$ is adjoined, therefore ignored by LA
	  \item $\eta$ is interpreted as the conjunction of {\rm Mario} and {\rm running}
	    \begin{itemize}
	      \item This is an ill-formed interpretation.
	      \item Possibly an i-within-i violation \parencite{vergnaud1974french}
	    \end{itemize}
	\end{itemize}
      \end{block}
    \end{column}
    \begin{column}[T]{0.45\textwidth}
      {\small
	  \begin{forest}
	    nice empty nodes,sn edges,baseline
	    [$\alpha$
	      [{\rm I}]
	      [$\beta$
		[Voice]
		[$\gamma$
		  [$\zeta$
		    [{\rm see}]
		    [{\rm Bill}]
		  ]
		  [$\eta$
		    [{\rm Mario}]
		    [Prog]
		  ]
		]
	      ]
	    ]
	  \end{forest}
	}
    \end{column}
  \end{columns}
\end{frame}
\end{document}


